Universal Anonymous Signatures

### 2022-10-05 prism-backend/research/gsac/app-related-extra.tex
Typos and notation fixed. Some important updates pending...

We cannot build the exact same functionality, nor follow the exact same security
model as in the group signatures with message dependent opening (GS-MDO) scheme
described in \cite{ehk+19}. Simply because, therein, the opening functionality
is divided in two authorities: the admitter, who decides which messages are
subject to be opened or not, and generates a token that enables opening
signatures over such messages; and the opener, who performs the actual opening,
but cannot do it without the tokens generated by the admitter. Intuitively,
this can be seen as a sort of ``distribution'' of the opening capability. We
define a variant in which the admitter and opener are combined
back into one entity (the opener), who can only open signatures over predefined
messages, but cannot open any other signature.
% Moreover, our variant directly supports the
% scenario of multiple such openers, each being able to open only signatures
% over different messages.
Note that it should still be possible to apply
thresholding techniques to extend this case so that our ``unified'' opener role
is shared across multiple entities, who have to cooperate in order to open a
signature \cite{cdl+20}, thus achieving something very close ``in spirit'' to
the scheme in \cite{ehk+19}. In addition, while \cite{ehk+19} follows the static
group signature setting, we move to the dynamic one.

@@

Note that, for simplicity and to build upon our \CUASGS construction, we
describe a variant where the set of messages to disallow is defined once via
$KeyGen$. However, separating this into a dedicated \OKeyGen function that can
be called multiple times, and thus allowing multiple openers, each with a
different set of disallowed messages, is trivial -- and again, our definition
of the \oracle{Open} oracle takes care of everything, as every challenge
signature is produced over the same opener key.

@@

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable as a $(\fissue^{single,H,I},\feval^{F,MPS},
\finsp^{G,MPS})$-\CUASGen restriction. Concretely, this restricts to a system
with one credential per user and no attributes in the credentials.

@@

On the other hand, anonymous issuance and the capability to customise issuance
policies are unachievable by MPS. Anonymous issuance simply does not make sense
in MPS, as it only supports one credential (without attributes) per user, and
customised issuance is achieved in \UAS via the \fissue functions, with no
equivalent in MPS -- instead, MPS can be seen as having the fixed policy of
``proving knowledge of a user secret key''. These extensions are not trivial
from a modelling point of view, and also have a big impact in the practicality
of the resulting system. Also, MPS does not include verifiable openings. While
this is easy to add, we consider it to be essential, given that the proposed
generalisation of opening allows the opener to output ``any value''. Hence, the
need to ensure that the produced value is the legitimate one seems to be more
necessary than ever. Finally, our \feval function is a generalisation of $F$ in
MPS, as it allows two outputs: one will be returned in the clear along with the
signature, and the other will be encrypted. Indeed, making part of the output
unencrypted allows implementing very useful variants such as anonymous
credentials with selective disclosure, as shown before.

@@

With these functions, the construction is direct. \CUASMPS's setup runs
\CUASGen's \Setup, \OKeyGen, and generates the issuer key pair by running
\KeyGen and \ISet (with $\fissue^{single,H,I}$). For MPS's join, \CUASMPS runs
first \KeyGen to generate the user key pair, and then proceeds as in \CUASGen.
\Sign, \Verify and \Open, are as in \CUASGen.

Finally, note that, in MPS, $G$ is further parameterised with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
key pair, and is an input of \finsp.

\paragraph{Security of \CUASMPS.} %
As stated, we restrict to privacy-1 of MPS (although, as
discussed, we actually achieve something slightly stronger). Unforgeability-1 in
MPS is implied by unforgeability in \UAS (where the latter also covers
unforgeability of \fissue evaluations, plus verifiable openings).
Unforgeability-2 in MPS is equivalent to non-frameability in \UAS (where the
latter also includes framing via verifiable openings). Finally note that, in
UAS, we do not explicitly model extractability, but rather make it an inherent
requirement in the unforgeability and non-frameability definitions. Thus, our
\CUASMPS construction also ensures MPS-extractability.

@@

\begin{proof}  
  Note that the privacy-1 game in MPS and the signature anonymity game in \UAS
  are, in essence, equivalent. Thus, given an adversary \adv~that breaks
  privacy-1 of \CUASMPS as defined for MPS, it is easy to build an adversary
  \advB breaking signature anonymity of the underlying \CUASGen, as defined in
  \UAS.

  \advB simply leverages its own oracles in order to answer oracle queries from
  \adv: $\mathcal{O}_{read},\mathcal{O}_{write},\mathcal{O}_{CU},\mathcal{O}_{HU},
  \mathcal{O}_{sig},\mathcal{O}_{open}$ in MPS correspond to \RREG, \WREG,
  \CUGEN, \HUGEN, \SIGN and \OPEN in \UAS, respectively. The output given by
  \adv~in the first stage of the MPS game is then directly used as input to
  \advB's \CHALb oracle. Finally, \advB outputs whatever \adv~outputs.

@@

  \advB simulates \adv's game essentially as in the privacy-1 proof. Note also
  that \adv~receives the issuer's secret key. This can be obtained by \advB via
  its \ICORR oracle. Eventually, \adv~outputs a $(F,M,\Sigma)$ tuple, which
  corresponds to $(\feval^{g,MPS},\msg,\Sig)$ (with $g=F$ in MPS) in \CUASGen,
  which \advB outputs in its own game. In addition, \advB outputs as $(\yinsp,
  \pi)$ values the output of \Open over $(\Sig,\msg)$ -- which internally
  computes $\finsp^{h,MPS}$, for $h=G$ in MPS.
  % 
  Note that the $\feval^{g,MPS}$ and $\finsp^{h,MPS}$ functions in \CUASMPS
  mimic the behaviour of MPS's $F$ and $G$, respectively. Thus, if \adv wins
  because $F$ returns $0$ when evaluated on the extracted values, then \advB
  wins at line 7 of the non-frameability game, as a legitimately computed
  $\feval^{g,MSP}$ function cannot output $0$. Similarly, if \adv~wins because
  the value returned by an honestly computed open function over the adversarial
  $(F,M,\Sigma)$ tuple does not match the output of $G$ over the extracted
  values, \advB wins at line 9: note that \advB returns the \yinsp value that
  \Open outputs (when computed honestly over \adv's output), whereas
  $\finsp^{g,MSP}=G$; thus, if both values differ in \adv's game, then they also
  differ in \advB's game.
  %
  \qed
\end{proof}

@@

  Simulation of \adv's oracles by \advB is again direct (as in previous proofs).
  Now, suppose that \adv~wins -- i.e., the identity extracted by \adv~does not
  belong to the set of corrupt users in \adv's game. By construction of \advB
  (identities in \adv's game map to a $\cid$ for \advB), $\OWNR[\cid] \notin
  \CU$ in \advB's unforgeability game either.
  % 
  However, in order for \advB to win in its own game, we need to prove also that
  the produced identity does not belong to a user in \HU either. Suppose that it
  does. Simulation extractability ensures that the credentials extracted by
  \adv~all belong to the same user (by assumption, in \HU) -- i.e., they are
  bound to its \usk. Moreover, since \adv~wins its game, the signature output by
  \adv~has not been obtained via its \SIGN oracle. But, given that the user is
  honest, its \usk has been produced uniformly at random, and has not been
  leaked to \adv~(as the issuer is also honest). Thus, the probability that
  the extracted credentials belong to an honest user is negligible and, if
  \adv~wins its game, \advB also does.
  %
  \qed
\end{proof}

@@

  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof.
  \advB outputs whatever \adv~outputs, adding a $(\yinsp,\iproof)$ pair, honestly
  generated from \adv's output. Note that the winning condition of \adv~
  requires that the produced signature belongs to an honest user, without
  having been produced via a call to the signing oracle. By construction of
  \advB, this directly makes \advB win in line 11 of the non-frameability game.
  %
  \qed
\end{proof}

@@

\subsubsection{\CUASRAC Construction.} %
Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,H,V,L},
\finsp^{F})$-\CUASGenInt restriction, where $\fissue^1$ is as in
\figref{fig:func-restrictions}, and $\feval^{\dattrs,H,V,L}$ and $\finsp^{H}$
are as specified in \esref{eq:funcs-rac}.

\begin{align}
  \feval^{\dattrs,H,V,L}(\upk,((\cidi,\cidu),\attrs),\cdot) \coloneqq &
    \nonumber \\
  & \hspace*{-10em} \pcif F(V,\cidi) \in L \lor F(V,\cidu) \in L: \pcreturn \bot
  \nonumber \\
  & \hspace*{-10em} \pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V) \nonumber \\
  \finsp^{F}((\cdot,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
  \coloneqq  & \nonumber \\
  & \hspace*{-10em} \pcreturn (F(\yeval^1,\cidi),F(\yeval^1,\cidu))
  \label{eq:funcs-rac}
\end{align}

Concretely, $\feval^{\dattrs,H,V,L}$ is defined via a set of attributes \dattrs
to reveal (e.g., age, etc.), a PRF $F$, a string identifying the verifier $V$
and a list $L$ of revocation handles by $V$. Note that, these ``extra
parameters'' can be hardcoded, though: $F$ can be a fixed PRF for all verifiers,
\dattrs and $V$ are also fixed (per verifier), and $L$ can be updated per
verifier with some reasonable frequency -- e.g., daily -- so that the cost of
recomputing $\feval^{\dattrs,H,V,L}$ is not high.
%
Since credentials in \CUASGenInt have two identifiers (\cidi, chosen by the
issuer; and \cidu, chosen by the user), $\feval^{\dattrs,H,V,L}$ internally
computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval aborts.
Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
$\yeval^1 \gets V$. $\yeval^1$ is
then used by $\finsp^H$ to compute $\yinsp \gets (H(\yeval^1,\cidi),
H(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
%
In more detail, the algorithms are as follows:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGenInt.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from
  \CUASGenInt, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from \CUASGenInt,
  setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGenInt.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGenInt, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(\yeval,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
  \attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive $\langle\Sign,\Verify\rangle$ of \CUASGenInt,
  using $\feval^{\dattrs,H,V,L}$ as signature evaluation function, and
  $\finsp^F$ as open function. The \yeval value output by the verifier, when
  it accepts, is the $\yeval^0$ value produced by \Sign in \CUASGenInt.
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
  \utrans, and runs \Open from \CUASGenInt. This returns $(H(V,\cidi),
  H(V,\cidu))$, which the verifier can add to its revocation list $L$.
\end{description}

\paragraph{Security of \CUASRAC.} %
We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
has signature anonymity and is unforgeable.
%
As for \CUASAC, we reduce to security of \CUASGen rather than to
$\CUASGen^{int}$. The ``translation'' between \CUASGen and $\CUASGen^{int}$ is
again trivial.

\begin{theorem}[Anonymity of \CUASRAC]
  \label{thm:anon-cuasrac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
  according to \cite{fhs19}.
\end{theorem}

@@

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN (in this case,
  also keeping track of the queries, per verifier), respectively.
  Note that ``translating'' the inputs from the former into inputs for the
  latter is trivial. Also, observe that $ReqCredHandle$/\OPEN essentially
  refuses to open transcripts from challenge users (signatures, in the
  non-interactive equivalent), as $F(V,\ccidi_0) \neq F(V,\ccidi_1)$ (and,
  similarly, for $\ccidu_b$) with overwhelming probability (see the $\tyinsp
  \neq \yinsp$) check in \figref{fig:oracles2}. Obviously, if \adv~wins in its
  anonymity game, then so does \advB with the same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, and $F$ is one-way, then \CUASRAC is an
  unforgeable RAC scheme.
\end{theorem}

@@

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~wins its game via the winning condition of line 9 in the RAC
  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
  that the probability of \adv~winning its game via condition $h_0 \in L$ at
  line 11 is negligible, due to soundness of the NIZK for $\NIZKRel_{\Sign}$.
  Moreover, soundness of NIZK for $\NIZKRel^{\Sign}$ as well as one-wayness
  of $F$ ensure that, if $h_1 \notin L$, then $b_1 = 1$. Namely, even when given
  $F(V,\cidi),F(V,\cidu)$ for a credential identified by $(\cidi,\cidu)$ owned
  by an honest user, and some (potentially malicious) $V$, it is not possible to
  generate $F(V',\cidi)$ nor $F(V',\cidu)$, for $V'=V$.
  % 
  \qed
\end{proof}

Note that, if we aim at global credential (resp. user) revocation rather than
verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
pair (resp., \upk), and no assumption regarding $F$ is needed.

@@

We give a simple definition for a Delegatable Anonymous Credentials (DAC)
scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
our simple scheme built from \CUASGenInt does not ensure privacy of the
delegation chain, which means that only actions by users with the same
delegation chain are indistinguishable -- this can make sense, for instance,
for organisations composed by many members. Delegation chain privacy could be
achieved by making \feval output projective proofs like in \cite{bcc+09}, but we
leave that out of scope for brevity. Our simple scheme
does, however, ensure that a (not top-level) issuer can only delegate attributes
contained in a credential it owns. Also, for simplicity, we restrict to the case
of using one credential per signature/interactive credential presentation, and
assume that all parties use the same opener and \finsp function.
%
The syntax is thus defined almost as in \secref{ssec:related-models-ac},
i.e., we have a $Setup$ algorithm, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
$IssKeyGen$, as now, as in \cite{bcc+09} (and our \UAS model), issuers collapse
with users -- instead, we have an $KG$ and $ISet$ algorithms, with the same
meaning as in \UAS.
%
In the model for this setting, since there are multiple issuers, in addition
to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
for creating honest and corrupt issuers, which can be simulated via \HUGEN,
\CUGEN, \ISET and \ICORR in our \UAS model.
%
The issuance and sign anonymity properties are direct, constraining the
adversary to output challenge credentials and signatures with the same
delegation chain. For unforgeability, we still require that no adversary can
authenticate using a set of attributes that have not been issued to a corrupt
user. In addition, we require that for any successful authentication using a
level-$l$ credential, we can extract a chain of credentials of length $l$ such
that each level-$i$ credential can be used successfully to authenticate the
level-$(i+1)$ credential, all the way down to the level-$l$ credential, and the
attributes revealed in the level-$l$ authentication are contained in all the
credentials up the chain. For this extraction, we assume in the model the
existence of a helper function $(\ipk_0,\lbrace (\ipk_i,\cred_i)
\rbrace_{i\in[1,l]}) \gets ExtractChain(\utrans)$ that outputs a sequence of
public keys and credentials from the root issuer $\ipk_0$ to the actual
credential used to sign $(\ipk_l,\cred_l)$.

>>>>

We cannot build the exact same functionality, nor follow the exact same security
model as in the group signatures with message dependent opening (GS-MDO) scheme
described in \cite{ehk+19}. Simply because, therein, the opening functionality
is divided in two authorities: the admitter, who decides which messages are
subject to be opened or not, and generates a token that enables opening
signatures over such messages; and the opener, who performs the actual opening,
but cannot do it without the tokens generated by the admitter. Intuitively,
this can be seen as a sort of ``distribution'' of the opening capability. We
define a variant in which the admitter and opener are combined
back into one entity (the opener), who can only open signatures over predefined
messages, but cannot open any other signature.
% Moreover, our variant directly supports the
% scenario of multiple such openers, each being able to open only signatures
% over different messages.
Although we leave it for future work, note that it should still be possible to
apply thresholding techniques to extend this case so that our ``unified'' opener
role is shared across multiple entities, who have to cooperate in order to open
a signature \cite{cdl+20}, thus achieving something very close ``in spirit'' to
the scheme in \cite{ehk+19}. In addition, while \cite{ehk+19} follows the static
group signature setting, we move to the dynamic one.

@@

For simplicity and to build upon our \CUASGS construction, we
describe a variant where the set of messages to disallow is defined once via
$KeyGen$. However, separating this into a dedicated \OKeyGen function that can
be called multiple times, and thus allowing multiple openers, each with a
different set of disallowed messages, is trivial -- and again, our definition
of the \oracle{Open} oracle takes care of everything, as every challenge
signature is produced over the same opener key.

@@

Multimodal Private Signatures (or, rather, a close relative, see next) are
directly implementable as a $(\fissue^{single,H,I},\feval^{F,MPS},
\finsp^{G,MPS})$-\CUASGen restriction. Concretely, this restricts to a \UAS
system with one credential per user and no attributes in the credentials.

@@

On the other hand, anonymous issuance and the capability to customise issuance
policies are unachievable by MPS. Anonymous issuance simply does not make sense
in MPS, as it only supports one credential (without attributes) per user, and
customised issuance is achieved in \UAS via the \fissue functions, with no
equivalent in MPS -- instead, MPS can be seen as having the fixed policy of
``proving knowledge of a user secret key''. These extensions are not trivial
from a modelling point of view, and also have a big impact in the practicality
of the resulting system. Also, MPS does not include verifiable openings. While
this is easy to add, we consider it to be essential, given that the proposed
generalisation of opening allows the opener to output any value. Hence, the
need to ensure that the produced value is the legitimate one seems to be more
necessary than ever. Finally, our \feval function is a generalisation of $F$ in
MPS, as it allows two outputs: one will be returned in the clear along with the
signature, and the other will be encrypted. Indeed, making part of the output
unencrypted allows implementing very useful variants such as anonymous
credentials with selective disclosure, as shown before.

@@

With these functions, the construction is direct. \CUASMPS's setup runs
\CUASGen's \Setup, \OKeyGen, and generates the issuer key pair by running
\KeyGen and \ISet (with $\fissue^{single,H,I}$). For MPS's join, \CUASMPS runs
first \KeyGen to generate the user key pair, and then proceeds as in \CUASGen.
\Sign, \Verify and \Open, are as in \CUASGen -- where, in \Open, we simply
ignore the opening proof.

Finally, note that, in MPS, $G$ is further parameterised with a value $j$, which
essentially is the result of applying $F$ to the message and signer identity,
and is not leaked to the opener nor any other third party. The equivalent in
\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
key pair, and is an input to \finsp.

\paragraph{Security of \CUASMPS.} %
We restrict to privacy-1 of MPS (although, as
discussed, we actually achieve something slightly stronger). Unforgeability-1 in
MPS is implied by signature unforgeability in \UAS.
Unforgeability-2 in MPS is equivalent to non-frameability in \UAS (where the
latter also includes framing via verifiable openings). Finally note that, in
UAS, we do not explicitly model extractability, but rather make it an inherent
requirement in the unforgeability and non-frameability definitions. Thus, our
\CUASMPS construction also ensures MPS-extractability.

@@

\begin{proof}  
  Note that the privacy-1 game in MPS and the signature anonymity game in \UAS
  are, in essence, equivalent. Thus, given an adversary \adv~that breaks
  privacy-1 of \CUASMPS as defined for MPS, it is easy to build an adversary
  \advB breaking signature anonymity of the underlying \CUASGen construction, as
  defined in \UAS.

  \advB simply leverages its own oracles in order to answer oracle queries from
  \adv: $\mathcal{O}_{read},\mathcal{O}_{write},\mathcal{O}_{CU},\mathcal{O}_{HU},
  \mathcal{O}_{sig},\mathcal{O}_{open}$ in MPS correspond to \RREG, \WREG,
  \CUGEN, \HUGEN, \OBTAIN, \SIGN and \OPEN in \UAS, respectively. The output
  given by \adv~in the first stage of the MPS game is then directly used as
  input to \advB's \CHALb oracle. Finally, \advB outputs whatever \adv~outputs.

@@

  \advB simulates \adv's game essentially as in the privacy-1 proof. Note also
  that \adv~receives the issuer's secret key. This can be obtained by \advB via
  its \ICORR oracle. Eventually, \adv~outputs a $(F,M,\Sigma)$ tuple, which
  corresponds to $(\feval^{F,MPS},\msg,\Sig)$ in \CUASGen,
  which \advB outputs in its own game. In addition, \advB outputs as $(\yinsp,
  \pi)$ values the output of \Open over $(\Sig,\msg)$ -- which internally
  computes $\finsp^{G,MPS}$.
  % 
  Note that the $\feval^{F,MPS}$ and $\finsp^{G,MPS}$ functions in \CUASMPS
  mimic the behaviour of MPS's $F$ and $G$, respectively. Thus, if \adv wins
  because $F$ returns $0$ when evaluated on the extracted values, then \advB
  wins at line 7 of the non-frameability game, as a legitimately computed
  $\feval^{F,MSP}$ function cannot output $0$. Similarly, if \adv~wins because
  the value returned by an honestly computed open function over the adversarial
  $(F,M,\Sigma)$ tuple does not match the output of $G$ over the extracted
  values, \advB wins at line 9: note that \advB returns the \yinsp value that
  \Open outputs (when computed honestly over \adv's output), whereas
  $\finsp^{G,MSP}=G$; thus, if both values differ in \adv's game, then they also
  differ in \advB's game.
  %
  \qed
\end{proof}

@@

  Simulation of \adv's oracles by \advB is again direct (as in previous proofs).
  Now, suppose that \adv~wins -- i.e., the identity extracted by \adv~does not
  belong to the set of corrupt users in \adv's game. By construction of \advB
  (identities in \adv's game map to a \cid for \advB), $\OWNR[\cid] \notin
  \CU$ in \advB's unforgeability game either.
  % 
  However, in order for \advB to win in its own game, we need to prove also that
  the produced identity does not belong to a user in \HU either. Suppose that it
  does. Simulation extractability ensures that the credentials extracted by
  \adv~all belong to the same user (by assumption, in \HU) -- i.e., they are
  bound to its \usk. But, since \adv~wins its game, the signature output by
  \adv~has not been obtained via its \SIGN oracle. But, given that the user is
  honest, its \usk has been produced uniformly at random, and has not been
  leaked to \adv~(as the issuer is also honest). Thus, the probability that
  the extracted credentials belong to an honest user is negligible and, if
  \adv~wins its game, \advB also does.
  %
  \qed
\end{proof}

@@

  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof
  (leveraging the \OBTAIN oracle instead of \OBTISS or \ISSUE).
  \advB outputs whatever \adv~outputs, adding a $(\yinsp,\iproof)$ pair, honestly
  generated from \adv's output. Note that the winning condition of \adv~
  requires that the produced signature belongs to an honest user, without
  having been produced via a call to the signing oracle. By construction of
  \advB, this directly makes \advB win in line 11 of the non-frameability game.
  %
  \qed
\end{proof}

@@

\subsubsection{\CUASRAC Construction.} %
Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,H,V,L},
\finsp^{H})$-\CUASGenInt restriction, where $\fissue^1$ is as in
\figref{fig:func-restrictions}, and $\feval^{\dattrs,H,V,L}$ and $\finsp^{H}$
are as specified in \esref{eq:funcs-rac}.

\begin{align}
  \feval^{\dattrs,H,V,L}(\upk,((\cidi,\cidu),\attrs),\cdot) \coloneqq &
    \nonumber \\
  & \hspace*{-10em} \pcif H(V,\cidi) \in L \lor H(V,\cidu) \in L: \pcreturn \bot
  \nonumber \\
  & \hspace*{-10em} \pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V) \nonumber \\
  \finsp^{H}((\cdot,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
  \coloneqq  & \nonumber \\
  & \hspace*{-10em} \pcreturn (H(\yeval^1,\cidi),H(\yeval^1,\cidu))
  \label{eq:funcs-rac}
\end{align}

Concretely, $\feval^{\dattrs,H,V,L}$ is defined via a set of attributes \dattrs
to reveal, a PRF $H$, a string identifying the verifier $V$
and a list $L$ of revocation handles by $V$. Note that, these ``extra
parameters'' can be hardcoded, though: $H$ can be a fixed PRF for all verifiers,
\dattrs and $V$ are also fixed (per verifier), and $L$ can be updated per
verifier with some reasonable frequency -- e.g., daily -- so that the cost of
recomputing $\feval^{\dattrs,H,V,L}$ is not high (of course, revocation of a
credential is not effectuve until $L$, and the function, is updated).
%
Since credentials in \CUASGenInt have two identifiers (\cidi, chosen by the
issuer; and \cidu, chosen by the user), $\feval^{\dattrs,H,V,L}$ internally
computes $H(V,\cidi)$ and $H(V,\cidu)$. If either appears in $L$, \feval aborts.
Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
$\yeval^1 \gets V$. $\yeval^1$ is
then used by $\finsp^H$ to compute $\yinsp \gets (H(\yeval^1,\cidi),
H(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$,
and add it to its list $L$.
%
In more detail, the algorithms are as follows:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGenInt.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from
  \CUASGenInt, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from \CUASGenInt,
  setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGenInt.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGenInt, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(\yeval,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
  \attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive $\langle\Sign,\Verify\rangle$ of \CUASGenInt,
  using $\feval^{\dattrs,H,V,L}$ as signature evaluation function, and
  $\finsp^H$ as open function. The \yeval value output by the verifier, when
  it accepts, is the $\yeval^0$ value produced by \Sign in \CUASGenInt.
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
  \utrans, and runs \Open from \CUASGenInt. This returns $(H(V,\cidi),
  H(V,\cidu))$, which the verifier can add to its revocation list $L$.
\end{description}

\paragraph{Security of \CUASRAC.} %
We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
scheme, according to the model in \figref{fig:model-rac}, if the underlying
\CUASGen construction has signature anonymity and is unforgeable.
%
As for \CUASAC, we reduce to security of \CUASGen rather than to
\CUASGenInt. The ``translation'' between \CUASGen and \CUASGenInt is
again trivial.

\begin{theorem}[Anonymity of \CUASRAC]
  \label{thm:anon-cuasrac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
  according to the model in \figref{fig:model-rac}.
\end{theorem}

@@

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to \oracle{HU}, \oracle{CU}, \oracle{Obtain},
  \oracle{Show}, \oracle{LoR}, \oracle{ReqCredHandle}, \advB
  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN (in this case,
  also keeping track of the queries, per verifier), respectively.
  Note that ``translating'' the inputs from the former into inputs for the
  latter is trivial. Also, observe that $ReqCredHandle$/\OPEN essentially
  refuses to open transcripts from challenge users (signatures, in the
  non-interactive equivalent), as $F(V,\ccidi_0) \neq F(V,\ccidi_1)$ (and,
  similarly, for $\ccidu_b$) with overwhelming probability (see the $\tyinsp
  \neq \yinsp$) check in \figref{fig:oracles2}. Obviously, if \adv~wins in its
  anonymity game, then so does \advB with the same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has signature unforgeability according to
  \defref{def:sign-forge-uas}, and $H$ is a secure PRF, then \CUASRAC is an
  unforgeable RAC scheme.
\end{theorem}

@@

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof
  (leveraging \OBTISS and \ISSUE oracles instead of \OBTAIN). Assume that \adv~
  wins its game via the winning condition of line 9 in the RAC unforgeability
  game. The same reasoning as in \CUASAC applies here. Next, note that the
  probability of \adv~winning its game via condition $h_0 \in L$ at line 11 is
  negligible, due to simulation extractability of the NIZK for \RelSig.
  Moreover, simulation extractability of the NIZK for \RelSig as well as
  randomness of $H$ ensure that, if $h_1 \notin L$, then $b_1 = 1$. Namely, even
  when given $H(V,\cidi),H(V,\cidu)$ for a credential identified by
  $(\cidi,\cidu)$ owned by an honest user, and some (potentially malicious) $V$,
  it is not possible to generate $H(V',\cidi)$ nor $H(V',\cidu)$, for $V'=V$.
  % 
  \qed
\end{proof}

Note that, if we aim at global credential (resp. user) revocation rather than
verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
pair (resp., \upk), and no assumption regarding $H$ is needed.

@@

We give a simple definition for a Delegatable Anonymous Credentials (DAC)
scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
our simple scheme built from \CUASGenInt does not ensure privacy of the
delegation chain, which means that only actions by users with the same
delegation chain are indistinguishable -- this can make sense, for instance,
for organisations composed by many members. Delegation chain privacy could be
achieved by making \feval output projective proofs like in \cite{bcc+09} (or,
to some extent, building on \CUASGenHideIss rather than on \CUASGen), but we
leave that out of scope for brevity. Our simple scheme
does, however, ensure that a (not top-level) issuer can only delegate attributes
contained in a credential it owns. Also, for simplicity, we restrict to the case
of using one credential per signature/interactive credential presentation, and
assume that all parties use the same opener and \finsp function.
%
The syntax is thus defined almost as in \secref{ssec:related-models-ac},
i.e., we have a $Setup$ algorithm, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
$IssKeyGen$, as now, as in \cite{bcc+09} (and our \UAS model), issuers collapse
with users -- instead, we have an $KG$ and $ISet$ algorithms, with the same
meaning as in \UAS.
%
In the model for this setting, since there are multiple issuers, in addition
to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
for creating honest and corrupt issuers, which can be simulated via \HUGEN,
\CUGEN, \ISET and \ICORR in our \UAS model.
%
The issuance and sign anonymity properties are direct, constraining the
adversary to output challenge credentials and signatures with the same
delegation chain. For unforgeability, we still require that no adversary can
authenticate using a set of attributes that have not been issued to a corrupt
user. In addition, we require that for any successful authentication using a
level-$l$ credential, we can extract a chain of credentials of length $l$ such
that each level-$i$ credential can be used successfully to authenticate the
level-$(i+1)$ credential, all the way down to the level-$l$ credential, and the
attributes revealed in the level-$l$ authentication are contained in all the
credentials up the chain. For this extraction, we assume in the model the
existence of a helper function $(\ipk_0,\lbrace (\ipk_i,\cred_i)
\rbrace_{i\in[1,l]}) \gets \helper{ExtractChain}(\utrans)$ that outputs a
sequence of public keys and credentials from the root issuer $\ipk_0$ to the
actual credential used to sign $(\ipk_l,\cred_l)$.
